---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Title

Authors: Madison Kraft, Luke Engstrom

Co-Author: Dr. Christopher Merkord

Affiliations: Minnesota State University of Moorhead

## Abstract

-   Manta ray migrate where the food is, which makes them hard to study

-   In addition, they are at risk from fisheries and bycatch

-   Using iNaturalist data to see if there are migration patterns

-   Then identifying breeding grounds of two different species of manta ray

-   With this information we propose to make these sites protected grounds

## Introduction

Manta ray are an elusive species and recently more information has been found on the organism. Due to only selective individuals being documented through out history, it is important to understand and protect these fish. One way is by identifying potential breeding grounds and tracking migration patterns and advocate for protected fishing zones.

There are two specific ray species we will be looking at the Mobula birostris (Ocean ray) and Mobula alfredi (reef ray). Both of these organisms have limited knowledge on their juvenile stage, individual juveniles have never been successfully studied in the wild (Stewart et al 2018).

## Methods

-   Using iNaturalist data, a citizen science program used to catalog sightings of organisms

-   Then cleaned up the data using rNat and tidyverse

-   We filtered the data to include species name, latitude, longitude, year, month, and day

-   Then made a map with the filtered data

## Results

Figure 1. World map depicting the sightings

```{r World}
library(rinat)
library(tidyverse)

indx <- setNames( rep(c('winter', 'spring', 'summer',
                        'fall'),each=3), c("12","01","02","03","04","05","06","07","08","09","10","11"))

Oceanic_Ray <- 
  get_inat_obs(query = "Oceanic Manta Ray",maxresults = 1000) %>% 
  as_tibble() %>% 
  select(scientific_name, time_observed_at, latitude, longitude) %>% 
  filter(scientific_name == "Mobula birostris",time_observed_at != "") %>% 
  mutate(
    year = substr(time_observed_at,0,4),
    month = substr(time_observed_at,6,7),
    day = substr(time_observed_at,9,10),
    season = indx[as.character(month)]
    )%>% 
  print()

Reef_Ray <- 
  get_inat_obs(query = "Reef Manta Ray",maxresults = 1000) %>% 
  as_tibble() %>% 
  select(scientific_name, time_observed_at, latitude, longitude) %>% 
  filter(scientific_name == "Mobula alfredi",time_observed_at != "") %>% 
  mutate(
    year = substr(time_observed_at,0,4),
    month = substr(time_observed_at,6,7),
    day = substr(time_observed_at,9,10),
    season = indx[as.character(month)]
  )%>% 
  print()

Combined_Table <- rbind(Oceanic_Ray,Reef_Ray) %>% 
  select(scientific_name, latitude, longitude, year, month,day) %>% 
  print()

world <- map_data("world")

ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region)
  ) +
  geom_point(data = Reef_Ray,
             mapping = aes(x = longitude, y = latitude,
                           color = season,
                           size = ".01",
                           alpha = .01))
```

## Discussion

-   Weather patterns have not impacted the sightings as much as we thought

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
