---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Title

Authors: Madison Kraft, Luke Engstrom

Co-Author: Dr. Christopher Merkord

Affiliations: Minnesota State University of Moorhead

## Abstract

bullet points (3 to 5 points) and 10 - 15 words per bullet

-   Using iNaturalist data to see if there are migration patterns

-   Then identifying breeding grounds of two different species of manta ray

## Introduction

Manta ray are an elusive species and recently more information has been found on the organism. Due to only selective individuals being documented through out history, it is important to understand and protect these fish. One way is by identifying potential breeding grounds and tracking migration patterns and advocate for protected fishing zones.

There are two specific ray species we will be looking at the Mobula birostris (Ocean ray) and Mobula alfredi (reef ray). Both of these organisms have limited knowledge on their juvenile stage, individual juveniles have never been successfully studied in the wild (Stewart et al 2018).

## Methods

We are using iNaturalist a citizen science program used to catalog natural sightings of organisms in the effort to identify the individual. By using the rNat package, we filtered the data to include species name, latitude, longitude, year, month, and day of both ocean ray and reef ray. Then taking the filtered data, we will make a map of the world and use the latitude and longitude to mark the area of the sighting.

## Results

You

```{r cars}
summary(cars)
```

## Discussion

You

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
